\bf Eye Fitting Straight Lines in the Modern Era

### 2022-02-07 Eye-Fitting-Straight-Lines-in-the-Modern-Era.Rmd
adjusted minor wording

Initial studies in the 20th century explored the use of fitting lines by eye through a set of points [@finney1951subjective; @mosteller1981eye]. 
Common methods of fitting trends by eye involved maneuvering a string, black thread, or ruler until the fit is suitable, then drawing the line through the set of points. Recently, @ciccione2021can conducted a comprehensive set of studies investigating human ability to detect trends in graphical representations \ear{using manual adjustment and manipulation methods.}
<!-- \svp{using these types of manipulations.}  -->
<!-- \ear{XXX this study was conducted online, but asked users to use the arrows on their keyboard to adjust the slope or select whether the shown slope was positive or negative}. -->

>>>>

Initial studies in the 20th century explored the use of fitting lines by eye through a set of points [@finney1951subjective; @mosteller1981eye]. 
Common methods of fitting trends by eye involved maneuvering a string, black thread, or ruler until the fit is suitable, then drawing the line through the set of points. Recently, @ciccione2021can conducted a comprehensive set of studies investigating human ability to detect trends in graphical representations \ear{using physical adjustment and manipulation methods.}
<!-- \svp{using these types of manipulations.}  -->
<!-- \ear{XXX this study was conducted online, but asked users to use the arrows on their keyboard to adjust the slope or select whether the shown slope was positive or negative}. -->

### 2022-02-07 Eye-Fitting-Straight-Lines-in-the-Modern-Era.tex
adjusted minor wording

Initial studies in the 20th century explored the use of fitting lines by
eye through a set of points
\citep{finney1951subjective, mosteller1981eye}. Common methods of
fitting trends by eye involved maneuvering a string, black thread, or
ruler until the fit is suitable, then drawing the line through the set
of points. Recently, \citet{ciccione2021can} conducted a comprehensive
set of studies investigating human ability to detect trends in graphical
representations
{\textcolor{blue}{using manual adjustment and manipulation methods.}}

>>>>

Initial studies in the 20th century explored the use of fitting lines by
eye through a set of points
\citep{finney1951subjective, mosteller1981eye}. Common methods of
fitting trends by eye involved maneuvering a string, black thread, or
ruler until the fit is suitable, then drawing the line through the set
of points. Recently, \citet{ciccione2021can} conducted a comprehensive
set of studies investigating human ability to detect trends in graphical
representations
{\textcolor{blue}{using physical adjustment and manipulation methods.}}
